---
title: "reprex"
author: "Allison Horst"
date: "8/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
```

Your job is to identify an error, then make a reproducible example that would help future you or someone else understand how to write the code correctly. In other words, your reprex code will *work* and offer a solution to the error thrown in each of the following examples. 

Data are in `AS00601.csv` (and read in correctly below as `mack_creek_vertebrates`). 

Data package title: Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present

**Citation:** Gregory, S.V. and I. Arismendi. 2020. Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present ver 14. Environmental Data Initiative. https://doi.org/10.6073/pasta/7c78d662e847cdbe33584add8f809165

### Read in the data 

There are no problems here. 
```{r}
mack_creek_vertebrates <- read_csv(here("AS00601.csv"))
```

### reprex 1

Identify what is causing the problem in the code below (there's only one thing). Then, create a very simple reprex that would help yourself, future you, or a colleague fix the problem. **Post your reprex as an issue in your own fork on GitHub.**

```{r}
# Example 1: 
mack_creek_lengths <- mack_creek_vertebrates %>% 
  clean_names() %>% 
  select(year:sampledate) %>% 
  filter(section == "CC") %>% 
  mutate(across(.cols = where(is.character), .fns = tolower)) %>% 
  drop_na(species) %>% 
  group_by(species) %>% 
  summarize(mean_length_cm = mean(length1, na.rm = TRUE),
            sd_length_cm = sd(length1, na.rm = TRUE)) %>% 
  ungroup()
```

```{r}
library(here)
library(tidyverse)
library(janitor)

df <- tribble(
  ~Names, ~Hike, ~Length, 
  "Joe", "SB", 40, 
  "Halina", "GC", 21, 
  "Mia", "YS", 15
) 
df

df %>% clean_names() %>% 
  mutate(across(.fns = tolower, .cols = where(is.character)))
# To use the across function make sure you identify what each argument is or write them  in the correct order for the definition of the function. 

```


### reprex 2

Identify what is causing the problem in the code below (there's only one thing). Then, create a very simple reprex that would help yourself, future you, or a colleague fix the problem. **Post your reprex as an issue in your own fork on GitHub.**

```{r}
# Example 2:
df_mack <- mack_creek_vertebrates %>% 
  clean_names() %>% 
  filter(species == "ONCL")


ggplot(df_mack, aes(x = length1, y = weight)) +
  geom_point(shape = 12, color = "purple") +
  theme_minimal() +
  labs(x = "Cutthroat trout length (cm)",
       y = "Weight (g)")
```

```{r}
library(tidyverse)
library(here)
library(palmerpenguins)

penguins %>% clean_names %>% 
  filter(species == "Chinstrap") %>% 
  ggplot(aes(x = body_mass_g, y = flipper_length_mm))+
  geom_point(shape = 12, color = "black") 
# The only things that go into aes() when creating plots in r are variables from the data frame. The remainder of the customizations should be outside of aes(). 
```


## End